To each of my supervisors Kristen and Ren\'e for their ongoing support over the
years. Both professionally and monetarily. That support along with the wealth
of opportunities that they provided for me to lead, collaborate, and
present my work all over the world has been a continuous source of motivation
without which I would never have reached this point. Thank you.

To Bob Abraham for his overly enthusiastic approach to teaching AST
121: the Origin and Evolution of the Universe. The energy in his instruction
and his obvious love for astronomy was enough to convince teenage Ryan to
transfer into an astronomy major nearly a decade ago. 

To the many astronomy grad students that I've had the pleasure of working with
over the past five years, be it on research projects, shared TA duties, or
through outreach activities like Astrotours. As I said, it's been a pleasure.
Extra special thanks goes out my past office mates for their company and
(mostly) professional conduct at work.
Extra extra special thanks goes out the grad students with whom I shared a
cohort: Alex, Dana, Epson,
George, Nilou, Rob (sort of), Sasha, and Siqi. Thanks particularly for the many months
of qualifying exam prep sessions. Without all of their support during those
sessions I'm not sure where I'd be.

To the supporting cast of
astrophysicists, geneticists, and other UofT grad students on all of the
hockey, soccer, and softball teams. Thank you for helping me to balance my work
and life with those late night games and playoff pushes.

To my friends outside of school: Brendon, Chris, Jesse, Lien, Sarah, and
Solomon.
Thank you for all of the random get-togethers for birthday bbqs, band practices,
outdoor hockey games downtown, game nights, Caribbean cruises, my wedding... 
In the years leading up to and continuing throughout this degree, these things
have again helped me to maintain a certain balance that has undoubtedly helped
me get to this point.

To my family especially. To my Mom for---as she says---giving me all of
her physics
brain cells that she didn't need back when she was in school. To my Dad for
always fostering an environment in which learning and striving to be
successful in school and in work was of the highest priority. And not to
Chevonne.

Lastly to my wife, Alyssa. For cooking lots of my meals. For cleaning up after those
meals. For taking care of me when I get sick and taking me to the hospital at 3
in the morning because my leg feels weird. For the breakaway passes.
For continuing to put up with my brooding. For not waking me up after every
dream you have where I do something wrong. For already a year and a half of
marriage! And for coming with me to Boston. I'm really looking forward to it.
